Programming Language Foundations in Agda

### 2019-07-15 papers/scp/PLFA.tex
Updated SCP paper

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ierusalimschy; ten three-hour
  slots, comprising two hours of lecture followed by one hour of lab.
  Ten students completed the course, mostly doctoral students.  The
  course covered Parts~I and~II of PLFA, save students read chapter
  Lists on their own, and chapter Bisimilarity was skipped.

@@

For the courses run at Edinburgh and PUC-Rio, the scores vary
widely on the mock, but all students achieve perfection on the
exam.  (The one exception was a PUC-Rio student who did not attend
classes or sit the mock.)  Similar results were achieved at Edinburgh
over the previous five years, using SF as the course textbook and Coq
as the proof assistant.  We consider these results a tribute to the
students' ability to study and learn.

>>>>

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ieuramalischy; ten three-hour
  slots, comprising two hours of lecture followed by one hour of lab.
  Ten students completed the course, mostly doctoral students.  The
  course covered Parts~I and~II of PLFA, save students read chapter
  Lists on their own, and chapter Bisimilarity was skipped.

@@

Table~\ref{tab:exams} shows performance on the mock exam and the final
exam for the courses run at Edinburgh and PUC-Rio.  While scores vary
widely on the mock, all students achieve perfection on the
exam.  (The one exception was a PUC-Rio student who did not attend
classes or sit the mock.)  Similar results were achieved at Edinburgh
over the previous five years, using SF as the course textbook and Coq
as the proof assistant.  We consider these results a tribute to the
students' ability to study and learn.

\begin{table}
\begin{center}
  \begin{tabular}{|cc|cc|}
    \hline
    \multicolumn{2}{|c|}{Edinburgh} &
    \multicolumn{2}{c|}{PUC-Rio} \\
    \hline
    Mock & Exam & Mock & Exam \\
    \hline
     15  &  50  &  --  &  40  \\
     29  &  50  &  ~6  &  50  \\
     33  &  50  &  20  &  50  \\
     35  &  50  &  28  &  50  \\
     36  &  50  &  41  &  50  \\
     48  &  50  &  49  &  50  \\
     49  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
    \hline
  \end{tabular}
\end{center}
\caption{Exam marks}
\label{tab:exam}
\end{table}
